Development Of Parallel Matrix Operations

### 2011-02-15 paper/paper.tex
Added proper description to Gaussian elimination.

Describe the problem of matrix-vector multiplication and introduce the terms.

@@

To solve a linear system of equations of the form $Ax=b$, where $A$ is an $m\times n$ matrix, $b$ is an $m\times 1$ vector, and $x$ is the $m\times 1$ solution vector, first the matrix must be inverted. For most matrices, this presents a problem, as the inverse of a matrix is generally not easy to compute and may not even exist. Gaussian elimination is the process of performing a series of elementary row operations to the matrix $A$ to reduce it to a form, known as row-echelon form, that can be easily inverted.

>>>>

In the case of matrix-vector multiplication $A\cdot v$, the vector $\vec{v}$ is treated as a matrix of size $n\times 1$. As $\vec{v}$ is not of requisite size for the Strassen algorithm to be applied, only standard matrix-vector multiplication is used. Thus the process of computing this product is parallelized by dividing up the computation of dot products with the rows of $A$ and $\vec{v}$ among the threads.

@@

To solve a linear system of equations of the form 
\begin{equation}
$Ax=b$, 
\end{equation}
where $A$ is an $m\times n$ matrix, $b$ is an $m\times 1$ vector, and $x$ is the $m\times 1$ solution vector, first the matrix must be inverted. For most matrices, this presents a problem, as the inverse of a matrix is generally not easy to compute and may not even exist. Gaussian elimination is the process of performing a series of elementary row operations to the matrix $A$ to reduce it to a form, known as row-echelon form, that can be easily inverted. The matrix 
\begin{equation} 
\left[ \begin{array}{ccc|c}
a_{1,1} & a_{1,2} & a_{1,3} & b_1 \\
0 & a_{2,2} & a_{2,2} & b_2 \\
0 & 0 & a_{3,3} & b_3
\end{array} \right],
\end{equation}
where $a_{i,j}$ are the elements of $A$, and $b_i$ are the elements of $b$, is an example of the system $Ax=b$ in row-echelon form. Matrices in row-echelon form have the nice characteristic that all of the leading coefficients of each row are in a column whose number is less than the column of the leading coefficients in the rows below it and greater than those in the rows above it. In the process of Gaussian elimination with partial-pivoting, this is achieved by moving the row with the greatest leading coefficient above those with lesser coefficients, and then reducing the lower rows. In the case of square matrices whose rows are linearly independent, this reduction results in an upper-triangular form. Once the matrix is in this form, the inversion process is equivalent to back substituting the solution from the bottom of the matrix all the way to the top.
